### 2021-05-26 LaTeX-ACM/sections/paper.tex
minor edits

The final issue is who invokes \texttt{closeMarket()} every other block? There are actually two issues here: the issue of scheduling the function call and the issue of paying for it. For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next, we consider the second issue of who pays to close the market.

@@

\textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}. These technologies focus on fast transaction throughput, reducing gas costs, or educing transaction latency. When using \cm, we strive to reduce the gas cost as performance is the main bottleneck. Thus, we choose a Layer 2 technology called \textit{roll-up} which aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data. In a roll-up, every transaction is executed by a server or cluster of servers known as \textit{validators} that can be run by a collection of users or third party operators (here they can be run by the token issuer). These validators then push the result of the executions (\ie updates in the EVM state) back to the Ethereum and assure the Ethereum network that the transactions have been executed correctly.

>>>>

The final issue is who invokes \texttt{closeMarket()} every other block? There are two issues here: the issue of scheduling the function call and the issue of paying for it. For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next, we consider the second issue of who pays to close the market.

@@

\textit{Layer 2} solutions are a group of technologies that are designed and proposed to address specific drawbacks of executing transactions on \textit{Layer 1} (\ie Ethereum and other blockchains)~\cite{gudgeon2020sok}. These technologies focus on fast transaction throughput, reducing gas costs, and reducing transaction latency. When using \cm, we strive to reduce the gas cost as performance is the main bottleneck. Thus, we choose a Layer 2 technology called \textit{roll-up}. This technology aims at reducing the gas cost for operating on Layer 1 by taking the transaction executions off-chain and only using the Ethereum blockchain for storing data. In a roll-up, every transaction is executed by a server or cluster of servers known as \textit{validators} that can be run by a collection of users or third party operators (here they can be run by the token issuer). These validators then push the result of the executions (\ie updates in the EVM state) back to the Ethereum and assure the Ethereum network that the transactions have been executed correctly.
